The zoon R package for reproducible and shareable species distribution modelling

### 2017-01-31 ms.Rmd

Next we demonstrate how zoon can be used in practice for running SDMs, creating and sharing new modules, and performing a methods comparison. The workflow objects created by these analyses can be accessed at [`figshare.com/articles/zoon_applications_paper_workflows`](http://figshare.com/articles/zoon_applications_paper_workflows).
We encourage readers to download, interrogate and alter these workflows for themselves.

>>>>

Next we demonstrate how zoon can be used in practice for running SDMs, creating and sharing new modules, and performing a methods comparison. The workflow objects created by these analyses can be accessed at [`figshare.com/articles/zoon_applications_paper_workflows/4597792`](http://figshare.com/articles/zoon_applications_paper_workflows/4597792).
We encourage readers to download, interrogate and alter these workflows for themselves.
